Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-06-27 manuscripts/manuscript1.qmd
more prior stuff

---
title: Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention
author: "Nikhil Patel, MD"
subtitle: A Post Hoc Bayesian of ATACH-2 and ERICH data
authors:
  - name: Nikhil Patel
    orcid: 0000-0002-3193-8590
    affiliation: Department of Internal Medicine, Wake Forest University School of Medicine
    roles: data analysis, writing
    corresponding: true
  - name: Matt Jaffa
    affiliation: Department of Neurology, University of Connecticut School of Medicine
  - name: Rahul Karamchandani
    affiliation: Department of Neurology, Wake Forest University School of Medicine
  - name: Andrew Asimos
    affiliation: Department of Emergency Medicine, Wake Forest University School of Medicine
  - name: Jonathan Parish
    affiliation: Carolina Neurosurgery & Spine Associates
  - name: Nicholas Allen Morris
    affiliation: Department of Neurology, University of Maryland School of Medicine
date: last-modified
abstract: |

@@

```{r neurosurgery}
#| label: tbl-2
#| tbl-cap: "Association between hemispheric lateralization and care"
#| echo: false

# gather odds ratios and 95% credible intervals for each outcome
summary <- modelsummary(models,
  exponentiate = TRUE,
  fmt = 2,
  estimate = c("aOR" = "estimate"),
  statistic = c("95% Credible Interval" = "{conf.low} - {conf.high}"),
  coef_omit = "^(?!b_ich_lat)",
  coef_rename = c("b_ich_lateralityRight" = "Right Hemisphere ICH"),
  gof_map = c("none"),
  shape = model ~ term + statistic,
)

>>>>

---
title: Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention
author: "Nikhil Patel, MD"
subtitle: A Post Hoc Bayesian Analysis using data from ATACH-2 and ERICH
authors:
  - name: Nikhil Patel
    orcid: 0000-0002-3193-8590
    affiliation: Department of Internal Medicine, Wake Forest University School of Medicine
    roles: data analysis, writing
    corresponding: true
  - name: Matt Jaffa
    affiliation: Department of Neurology, University of Connecticut School of Medicine
  - name: Rahul Karamchandani
    affiliation: Department of Neurology, Wake Forest University School of Medicine
  - name: Andrew Asimos
    affiliation: Department of Emergency Medicine, Wake Forest University School of Medicine
  - name: Jonathan Parish
    affiliation: Carolina Neurosurgery & Spine Associates
  - name: Nicholas Allen Morris
    affiliation: Department of Neurology, University of Maryland School of Medicine
date: last-modified
abstract: |

@@

```{r neurosurgery}
#| label: tbl-2
#| tbl-cap: "Association between hemispheric lateralization and aggressive care"
#| echo: false
#| warning: false

# gather odds ratios and 95% credible intervals for each model
summary <- modelsummary(models,
  exponentiate = TRUE,
  fmt = 2,
  estimate = c("aOR" = "estimate"),
  statistic = c("95% Credible Interval" = "{conf.low} - {conf.high}"),
  coef_omit = "^(?!b_ich_lat)",
  coef_rename = c("b_ich_lateralityRight" = "Right Hemisphere ICH"),
  gof_map = c("none"),
  shape = model ~ term + statistic,
)
